\documentclass{now} % creates the journal version
% \documentclass{now}  % creates the book pdf version

% the now document class sets various dimensions, so be sure to *not* set
% or alter dimensions in your latex code.
% be sure to remove all manual formatting commands such \newpage, \clearpage.

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\newcommand{\figref}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Hao}[1]{$\clubsuit$\footnote{HAO: #1}}
% a few definitions that are *not* needed in general:
\newcommand{\ie}{\emph{i.e.}}
\newcommand{\eg}{\emph{e.g.}}
\newcommand{\etc}{\emph{etc}}
\newcommand{\now}{\textsc{now}}
\usepackage{times}
\usepackage[tight,footnotesize]{subfigure}
%\usepackage{bibspacing}
%\setlength{\bibspacing}{\baselineskip}

%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{verbatim}
%\usepackage{babel}  
\usepackage{listings}
\usepackage{comment} 
\usepackage{multirow}

%% Math Packages %%%%%%%%%%%%
\usepackage{amsthm}
\usepackage{amsfonts}


\title{High-Confidence Medical Device Software Development}
\author{
Zhihao Jiang and Rahul Mangharam \\
University of Pennsylvania\\
United States}

\begin{document}
\copyrightowner{Z.~Jiang and R.~Mangharam}
\volume{9}
\issue{4}
\pubyear{2015}
\copyrightyear{2015}
\isbn{978-1-68083-068-2}
\doi{10.1561/1000000040}
\firstpage{309}
\lastpage{391}
% the following settings can be set or left blank at first
%\copyrightowner{Z.~Jiang and R.~Mangharam}
% \volume{1}
% \issue{3}
% \pubyear{2014}
% \copyrightyear{2013}
% \isbn{978-0521833783}
% \doi{1234567890}
% \firstpage{23}
% \lastpage{94}

\frontmatter  % title page, contents, catalog information

\maketitle

\tableofcontents

\mainmatter

\begin{abstract}
The design of bug-free and safe medical device software is challenging, especially in complex implantable devices. This is due to the device's closed-loop interaction with the patient's organs, which are stochastic physical environments. The life-critical nature and the lack of existing industry standards to enforce software validation make this an ideal domain for exploring design automation challenges for integrated functional and formal modeling with closed-loop analysis. The primary goal of high-confidence medical device software is to guarantee the device will never drive the patient into an unsafe condition even though we do not have complete understanding of the physiological plant.

There are two major differences between modeling physiology and modeling man-made systems:
first, physiology is much more complex and less well-understood than man-made systems like cars and airplanes, and spans several scales from the molecular to the entire human body.
Secondly, the variability between humans is orders of magnitude larger than that between two cars coming off the assembly line.

Using the implantable cardiac pacemaker as an example of closed-loop device, and the heart as the organ to be modeled, we present several of the challenges and early results in model-based device validation. We begin with detailed timed automata model of the pacemaker, based on the specifications and algorithm descriptions from Boston Scientific. For closed-loop evaluation, a real-time Virtual Heart Model (VHM) has been developed to model the electrophysiological operation of the functioning and malfunctioning (i.e., during arrhythmia) hearts. By extracting the timing properties of the heart and pacemaker device, we present a methodology to construct timed-automata models for formal model checking and functional testing of the closed-loop system. The VHM's capability of generating clinically-relevant response has been validated for a variety of common arrhythmias. Based on a set of requirements, we describe a framework of Abstraction Trees that allows for interactive and physiologically relevant closed-loop model checking and testing for basic pacemaker device operations such as maintaining the heart rate, atrial-ventricle synchrony and complex conditions such as avoiding pacemaker-mediated tachycardia. 
\newpage
Through automatic model translation of abstract models to simulation-based testing and code generation for platform-level testing, this model-based design approach ensures the closed-loop safety properties are retained through the design toolchain and facilitates the development of verified software from verified models. This system is a step toward a validation and testing approach for medical cyber-physical systems with the patient-in-the-loop.

\end{abstract}

\input{A.tex}

\input{B.tex}

\input{C.tex}

%\input{D.tex}

\input{E.tex}

\input{F.tex}


\backmatter




\renewcommand{\bibname}{References}

\bibliographystyle{plainnat}
\bibliography{bibliography}

\end{document}